---
title: "GapMinder Analysis"
author: "Dave Guan"
date: "October 14, 2019"
output: 
  html_document:
    keep_md: yes
    fig_caption: yes
    toc: yes
---
# Introduction
 
change "html_document" to "pdf_document", after latex installation
Here's my first rmd document
table of content (toc) start with "#"

# Let's embed some R code

We'll write an R chunk that loads the tidyverse package and then read in the gapminder data set, use the back tip near "1" or ctrl+alt+i
```{r}
library(tidyverse)
gm<- read.csv("gapminder.csv")
```

#investigate gm data
let's take a look at GM

```{r}
head(gm)
```

#Our first plot

showing gdp per capia on x and life exp on y

```{r, fig.cap="Life expectancy vs GDP"}
ggplot(gm, aes(x=gdpPercap, y=lifeExp))+geom_point()
```

#A better plot

```{r, fig.cap="Life expectancy vs GDP"}
ggplot(gm, aes(x=gdpPercap, y=lifeExp))+geom_point(aes(col=continent))+scale_x_log10()
```

#possible chunk options
https://yihui.name/knitr/options/
options include: 
-echo (true by default, whether to include code in output)
-results
  -hide (hide the results)
  -hold (hold the result until end of chunk)
-include (true by default, if false then the code will not be run)
-fig.width, fig.height 
-cache (false by default) if true, will only re-run the code if any changes. result will be cached


```{r, fig.cap="Life expectancy vs GDP", fig.height=5, fig.width=10}
ggplot(gm, aes(x=gdpPercap, y=lifeExp))+geom_point(aes(col=continent))+scale_x_log10()
```


#table in RMarkdown
see some data using head
```{r}
head(gm)
```
now head function as a nicely formatted table

```{r}
library(knitr)
kable(head(gm))
```

